### 2024-08-19 paper/main.tex
spacing fixes
fixed citation, submitting to plos biology

Humans and animals attempt to maximize reward to time, select, and indicate a decision with a motor response\autocite*{drugowitschOptimalDecisionmakingTimevarying2014,balciOptimalTemporalRisk2011,bogaczPhysicsOptimalDecision2006,hudsonOptimalCompensationTemporal2008,trommershauserHumansRapidlyEstimate2006}. To obtain more reward, it has been shown that it is important to consider the inherent time delays and temporal uncertainties of the nervous system \autocite*{drugowitschTuningSpeedaccuracyTradeoff2015,balciOptimalTemporalRisk2011,hudsonOptimalCompensationTemporal2008,acerbiInternalRepresentationsTemporal2012,faisalNoiseNervousSystem2008,kordingBayesianDecisionTheory2006,wolpertMotorControlDecisionmaking2012,tanisAccuracyEffortCosts2023,lokeshVisualAccuracyDominates2023}. Past work has shown that humans will often produce nearly optimal decision times during cognitive\autocite*{balciOptimalTemporalRisk2011,mileticCautionDecisionmakingTime2019} and motor tasks\autocite*{hudsonOptimalCompensationTemporal2008,faisalOptimalCombinationSensory2009}. Other work has shown suboptimal action selection or timing, which has been suggested to occur from an imperfect representation of time delays or temporal uncertainties\autocite*{otaMotorPlanningTemporal2015,drugowitschComputationalPrecisionMental2016, onagawaSensorimotorStrategySelection2021, onagawaRiskAversion2019}. With time constraints, misrepresentations of inherent time delays or temporal uncertainties could lead to a missed deadline and consequently an indecision.

@@

\vspace{10mm}
\noindent \boldblue{Response Time Uncertainty}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%% Methods %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{2mm}
\SectionHeader{Methods}

>>>>

Humans and animals attempt to maximize reward to time, select, and indicate a decision with a motor response\autocite*{drugowitschOptimalDecisionmakingTimevarying2014,balciOptimalTemporalRisk2011,bogaczPhysicsOptimalDecision2006,hudsonOptimalCompensationTemporal2008,trommershauserHumansRapidlyEstimate2006}. To obtain more reward, it has been shown that it is important to consider the inherent time delays and temporal uncertainties of the nervous system \autocite*{drugowitschTuningSpeedaccuracyTradeoff2015,balciOptimalTemporalRisk2011,hudsonOptimalCompensationTemporal2008,acerbiInternalRepresentationsTemporal2012,faisalNoiseNervousSystem2008,kordingBayesianDecisionTheory2006,wolpertMotorControlDecisionmaking2012,tanisAccuracyEffortCosts2023,lokeshVisualAccuracyDominates2023}. Past work has shown that humans will often produce nearly optimal decision times during cognitive\autocite*{balciOptimalTemporalRisk2011,mileticCautionDecisionmakingTime2019} and motor tasks\autocite*{hudsonOptimalCompensationTemporal2008,faisalOptimalCombinationSensory2009}. Other work has shown suboptimal action selection or timing, which has been suggested to occur from an imperfect representation of time delays or temporal uncertainties\autocite*{otaMotorPlanningTemporal2015,drugowitschComputationalPrecisionMental2016, onagawaSensorimotorStrategySelection2021,onagawaRiskAversionAdjustment2019}. With time constraints, misrepresentations of inherent time delays or temporal uncertainties could lead to a missed deadline and consequently an indecision.

@@

% \vspace{10mm}
\noindent \boldblue{Response Time Uncertainty}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%% Methods %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\SectionHeader{Methods}
